First Exclusive Measurement of Deeply Virtual Compton Scattering off $^4$He: Toward the 3D Tomography of Nuclei

### 2017-10-03 eg6-letters/coherent/dvcs_he4_prl.tex
Implemented remarks from round 2 to coherent letter

There is an additional process contributing to the same final state as the 
DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of the electroproduction of 
a real photon includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target elastic form factors, which are well known in 
this kinematic region, while the DVCS amplitude depends on the GPDs. In our 
kinematics, the cross section of the real photon electroproduction is dominated 
by BH contribution, which varies strongly with $\phi$, the azimuthal angle 
between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
contribution is smaller by about a factor of two, but independent of $\phi$ at twist-2~%
\cite{Belitsky:2001ns}, and thus it is possible to separate these contributions 
with a cross section measurement. However, the DVCS-BH interference term offers 
an easier experimental access by generating spin asymmetries. We have, in 
particular, for a spin-zero target the beam spin asymmetry, $A_{LU}$, which 
can be expressed at leading-order and leading-twist~\cite{Kirchner:2003wt,
Belitsky:2008bz} as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
\end{split}
\label{eq:A_LU-coh}
\end{equation}
Explicit expressions of the kinematic factors $\alpha_i$ are derived 
from expressions in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$ and kinematical
factors. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

@@

\begin{figure*}[tb]
\includegraphics[width=16cm]{F_Coherent_ALU_phi_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian}, and the curves are the theoretical calculations 
   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
\label{fig:alu90}
\end{figure*}

@@

%conclusion
In summary, we have presented the first measurement of the beam-spin asymmetry
of exclusive coherent DVCS off $^4$He using the CLAS spectrometer supplemented 
with a RTPC. This setup allowed detection of the 
low-energy $^4$He recoils in order to ensure an exclusive measurement of the
coherent DVCS process. The azimuthal dependence of the measured $A_{LU}$ has 
been used to extract, in a model-independent way, the real and the imaginary 
parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in  
agreement with predictions of the available models. This first fully exclusive 
experiment opens new perspectives for studying nuclear structure with the GPD 
framework and paves the way for future measurements at JLab using 12 GeV CEBAF 
and upgraded equipment.

@@

>>>>

There is an additional process contributing to the same final state as the 
DVCS, the so-called Bethe-Heitler (BH) process, where the real photon is 
emitted by the incoming or the outgoing lepton. The DVCS and BH processes are 
indistinguishable experimentally and the amplitude of the electroproduction of 
a real photon includes a sum of the amplitudes of these two processes. The BH 
amplitude depends on the target elastic form factors, which are well known in 
this kinematic region, while the DVCS amplitude depends on the GPDs. In our 
kinematics, the cross section of the real photon electroproduction is dominated 
by BH contribution, which varies strongly with $\phi$, the azimuthal angle 
between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes. The DVCS 
contribution is smaller by about a factor of two, but independent of $\phi$ at twist-2~%
\cite{Belitsky:2001ns}, and thus it is possible to separate these contributions 
with a cross section measurement. However, the DVCS-BH interference term offers 
an easier experimental access by generating spin asymmetries. We have, in 
particular, for a spin-zero target the beam spin asymmetry, $A_{LU}$, which 
can be expressed at leading-order and leading-twist~\cite{Kirchner:2003wt,
Belitsky:2008bz} as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)}.
\end{split}
\label{eq:A_LU-coh}
\end{equation}
Where $F_A(t)$ is the nuclear form factor and explicit expressions of the 
kinematic factors $\alpha_i$ are derived from expressions in Ref.~\cite{Belitsky:2008bz}
These factors can be simplified as:
\begin{equation}
\begin{split}
&\alpha_0 (\phi)  = \frac{x_{A}(1+\epsilon^2)^2}{y} S_{++}(1) \sin(\phi) \\
&\alpha_1 (\phi)  =  c_0^{BH}+c_1^{BH} \cos({\phi})+c_2^{BH} \cos(2\phi) \\
&\alpha_2 (\phi)  =  \frac{x_{A}(1+\epsilon^2)^2}{y}  \left( C_{++}(0) +  
C_{++}(1) cos(\phi) \right) \\
&\alpha_3 (\phi) = \frac{x^{2}_{A}t(1+\epsilon^2)^2}{y} {\mathcal P}_1(\phi) 
{\mathcal P}_2(\phi) \cdot 2 \frac{2-2y+y^2 + \frac{\epsilon^2}{2}y^2}{1 + 
\epsilon^2}
\end{split}
\end{equation}
Where $S_{++}(1)$, $C_{++}(0)$ and $C_{++}(1)$ are the Fourier harmonics in the 
leptonic tensor, and with ${\mathcal P}_1(\phi)$ and ${\mathcal P}_2(\phi)$ the BH
propagators, which include only $\cos(\phi)$ dependencies. Their explicit 
expressions can be found in Appendix~A of \cite{Armstrong:2017wfw}.

 and are functions of Fourier harmonics in the 
azimuthal angle $\phi$,. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions, 
both the imaginary and real parts of $\mathcal{H}_{A}$ can be extracted unambiguously
by fitting the $A_{LU}(\phi)$ distribution.

@@

\begin{figure*}[tb]
\includegraphics[width=16cm]{F_Coherent_ALU_phi_90.pdf}
\caption{The $Q^{2}$ (left), $x_{B}$ (middle), and $t$-dependencies (right) of
   $A_{LU}$ at $\phi$~=~90$^{\circ}$ (black squares). On the 
   middle plot: the full-red and the dashed-blue curves are theoretical 
   calculations from \cite{simonetta_2}. On the right: the green circles are 
   the HERMES $-A_{LU}$ (a positron beam was used) inclusive measurements 
   \cite{Airapetian:2010nu}, and the curve is the theoretical calculation 
   from \cite{simonetta_2}. The grey bands represent the systematic errors.}
\label{fig:alu90}
\end{figure*}

@@

%conclusion
In summary, we have presented the first measurement of the beam-spin asymmetry
of exclusive coherent DVCS off $^4$He using the CLAS spectrometer supplemented 
with a RTPC. This setup allowed detection of the 
low-energy $^4$He recoils in order to ensure an exclusive measurement of the
coherent DVCS process. The azimuthal dependence of the measured $A_{LU}$ has 
been used to extract, in a model-independent way, the real and the imaginary 
parts of the $^4$He CFF, $\mathcal{H}_A$. The extracted CFF is in  
agreement with predictions of the available models. This first fully exclusive 
experiment opens new perspectives for studying nuclear structure with the GPD 
framework and paves the way for future measurements at JLab using 12 GeV CEBAF 
and upgraded equipment~\cite{Armstrong:2017wfw}.

@@

\bibitem{Armstrong:2017wfw} 
  W.~Armstrong {\it et al.},
  arXiv:1708.00888 [nucl-ex].
